Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-06-21 src/tex/ms.tex
Correct for less than sign

To investigate the performance of recalibration over the source parameter space,
we plot the improvement of mismatch in log projected over the parameter space of
$q$ vs. $\chi_{\mathrm{PN}}$ in Fig. \ref{fig:ps_q148_qchi}. On the mass ratio
axis, we can see the waveforms with $q\lq4$ show most consistent average
improvement. This is because that part of the parameter space is better covered
by the training waveform, as compared to testing waveforms from $q=4$ to $q=8$,
where some testing waveforms lie outside the source parameter space covered by
the training set of waveforms. On the spin axis, we can see the waveform with
$\chi_{\textrm{PN}}$ close to zero show the most consistent improvement, and we
start deviate from 0, there could be fluctuations in the average improvement. On
top of that, in the $q\lq4$ region, there seems to be more consistent
improvement of waveforms with $\chi_{\textrm{PN}}<0$. This can be understood as
since the original waveform was developed for aligned spin system, the waveforms
with $\chi_{\textrm{PN}}$ is less well-fitted \kw{Varify this.}, hence there
could be more room for improvement. To show this, we plot the parameter space of
$\chi_1$ vs. $\chi_2$ in Fig.~\ref{fig:ps_q148}. Waveforms along the diagonal
axis, i.e. $\chi_1\approx\chi_2$, show good mismatch improvements as discussed
above. Meanwhile, the top-left ($\chi_1<0<\chi_2$) and bottom-right
($\chi_1>0>\chi_2$) regions respond to optimization differently. In the top-left
region, waveforms generally improve slightly with along optimization. However,
waveforms in the bottom-right region do not improve after optimization. Some
waveforms even turned worse after optimization.

>>>>

To investigate the performance of recalibration over the source parameter space,
we plot the improvement of mismatch in log projected over the parameter space of
$q$ vs. $\chi_{\mathrm{PN}}$ in Fig. \ref{fig:ps_q148_qchi}. On the mass ratio
axis, we can see the waveforms with $q\le4$ show most consistent average
improvement. This is because that part of the parameter space is better covered
by the training waveform, as compared to testing waveforms from $q=4$ to $q=8$,
where some testing waveforms lie outside the source parameter space covered by
the training set of waveforms. On the spin axis, we can see the waveform with
$\chi_{\textrm{PN}}$ close to zero show the most consistent improvement, and we
start deviate from 0, there could be fluctuations in the average improvement. On
top of that, in the $q\le4$ region, there seems to be more consistent
improvement of waveforms with $\chi_{\textrm{PN}}<0$. This can be understood as
since the original waveform was developed for aligned spin system, the waveforms
with $\chi_{\textrm{PN}}$ is less well-fitted \kw{Varify this.}, hence there
could be more room for improvement. To show this, we plot the parameter space of
$\chi_1$ vs. $\chi_2$ in Fig.~\ref{fig:ps_q148}. Waveforms along the diagonal
axis, i.e. $\chi_1\approx\chi_2$, show good mismatch improvements as discussed
above. Meanwhile, the top-left ($\chi_1<0<\chi_2$) and bottom-right
($\chi_1>0>\chi_2$) regions respond to optimization differently. In the top-left
region, waveforms generally improve slightly with along optimization. However,
waveforms in the bottom-right region do not improve after optimization. Some
waveforms even turned worse after optimization.
